### 2018-10-18 manuscript.rmd
parsing partitions

```{r preliminaries}
library( tidyverse )
library( magrittr )
```

@@

@@

>>>>

```{r preliminaries}
library( tidyverse )
library( magrittr )
library(viridis)

source( "functions.R" )
```

@@

```{r taxonomy}

clades = c( "Fungi", "Ichthyosporea", "Filasterea", "Choanoflagellida", "Ctenophora", "Porifera", "Placozoa", "Bilateria", "Cnidaria" )

clade_colors = viridis( length(clades) )
names( clade_colors ) = clades

taxa = 
	read_tsv("taxonomy_info/taxon_table.tsv") %>% 
	distinct( relabelled_name, clade_assignment, ncbi_tax_id ) %>%
	dplyr::rename( taxon=relabelled_name, clade=clade_assignment )

@@

### Interpretting variation support

External criteria, eg posterior predictive scores, model fit etc
